
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res}

\usepackage{helvet} 

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Jackson Thapelo Moji} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
  % Your address
\moveleft.5\hoffset\centerline{(+27) 0838819463}
\moveleft.5\hoffset\centerline{jacksonmoji@gmail.com}
\moveleft.5\hoffset\centerline{https://jacksonmoji.tech}
\moveleft.5\hoffset\centerline{https://github.com/jacksonmoji}
\moveleft.5\hoffset\centerline{https://linkedin.com/in/jackson-thapelo-moji-5515167a}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS} 

{\sl Programming Languages:} \textbf{PHP, PHPUnit, Python, JavaScript, SQL} \\
{\sl Operations Technologies:}\textbf{ Vagrant, Git, Github} \\
{\sl Web Backend Technologies:} \textbf{ Apache, Django, MySQL, SQLite } \\
{\sl Web Frontend Technologies:} \textbf{ AngularJS, Bootstrap, SASS.} \\
{\sl Operating Systems:} \textbf{ Windows, Linux } \\
{\sl Familiar with:} \textbf{Docker, Jest, Netlify, ReactJS, C\#, Java, Flask, Laravel, MongoDB, PostgreSQL, Netlify, Heroku, AWS, MacOs} \\

%----------------------------------------------------------------------------------------
%	PROFESSIONAL PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{PROJECTS}

{\sl BantuWeb} \hfill 2019 \\
UCT MSc Project [ Angular|Django|AWS|PostgreSQL|Apache ]
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Bantuweb is a document discovery and crowd-sourcing platform developed in efforts to translate articles extracted from Wikipedia to indigenous South Africa languages in a gamified environment.
\item \textbf{http://ec2-52-87-247-222.compute-1.amazonaws.com}
\end{itemize}

{\sl Jacksonmoji} \hfill 2019 \\
Personal Project [ ReactJS|SASS|SQLite|Netlify ]
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and Developed a SPA for my personal digital presence.
\item \textbf{https://jacksonmoji.tech}
\end{itemize}


\section{EDUCATION}


{\sl MSc Computer Science } \hfill Current \\
University of Cape Town

{\sl BSc (Hons) Computer Systems Engineering } \hfill July 2015 \\
University of Sunderland


%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
  
 
\section{EXPERIENCE}

{\sl Software Engineer} \hfill November 2019 - Present \\
A24 Group | Remote
\begin{itemize}
\item Working on a legacy enterprise system for recruitment processes in the health industry. We are currently maintaining the
system which will be phased out over-time  to implement new and up to date
technologies using Node.js, React.js, and MongoDB from PHP and relational
databases (MySQL, MSSQL ).
\end{itemize} 

{\sl Software Engineer | Business Process Engineer} \hfill Feb - November 2019 \\
Thought Express | Cape Town, South Africa
\begin{itemize}
\item Led data migration/conversion from client's Oracle
DBMS to Thought Express's System.
\item Lead the business requirements analysis, design, development and
quality assurance of technical/business solutions.

\item Reviewed and re-designed existing processes to provide faster and
more effective solutions.

\item Engaged with clients in understanding the particular business needs/problems they needed to solve in relation to their business processes.

\item Combined analytical thinking with process understanding to meet and
solve problems.

\item Collaborated internally with the project team to design and build the
proposed business process solution.

% \item Worked individually towards my own deadlines while simultaneously
% engaging with the team in achieving collective goals and deadlines.
\end{itemize} 

{\sl Web Developer ( Contract ) } \hfill October 2018 - January 2019 \\
SQLI | Cape Town, Western Cape 
\begin{itemize} 
\item Developed extensions and applications in PHP for Magento E-Commerce apps built for clients.
\item Performed code reviews and design reviews from team members.
\item Performed troubleshooting and fixed tickets issued in Jira.
\item Wrote and reviewed team mates' PHP unit tests.
\item Worked with customer service to correct issues identified by users.
\end{itemize} 

{\sl Junior Software Developer} \hfill June 2015 - March 2017 \\
Open Software | Gaborone, Botswana
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and developed a Field Technician's Service Management Software using Laravel, MySQL, VueJs, Bootstrap, and Gitlab for Gaborone Electronics.
\item Maintained an Insurance Management System Developed using Symphony, JavaScript, and Bootstrap for a FSG Botswana.
\end{itemize}
 
%----------------------------------------------------------------------------------------

\end{resume}
\end{document}